---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regressionLinear

<!-- badges: start -->
[![R-CMD-check](https://github.com/GuoJennifer/regressionLinear/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/GuoJennifer/regressionLinear/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/GuoJennifer/regressionLinear/graph/badge.svg)](https://app.codecov.io/gh/GuoJennifer/regressionLinear)
<!-- badges: end -->

The goal of regressionLinear is to replicate at least some functionality of the lm() function in R, as a demonstration of how to create a complete R package.

Currently, the package contains only one function, "lr_coefficients", which will calculate the estimated coefficients for an SLR or MLR linear regression model, as well as the standard errors, and the t-tests with p-values for each covariate.

## Installation

You can install the development version of regressionLinear from [GitHub](https://github.com/) with:
```{r}
#install.packages("devtools")
devtools::install_github("GuoJennifer/regressionLinear")
```

Alternatively, you can use:

```{r}
#install.packages("pak")
pak::pak("GuoJennifer/regressionLinear")
```

## Example

This is a basic example of how to use the function "lr_coefficients" in this package:

```{r example}
library(regressionLinear)

regressionLinear::lr_coefficients("mpg", c("cyl", "disp", "hp"), data=mtcars)

```

