---
title: "lr_coefficients"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lr_coefficients}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r setup}
library(regressionLinear)
```

"lr_coefficients" is a function which will calculate the estimated coefficients for an SLR or MLR linear regression model, as well as the standard errors, and the t-tests with p-values for each covariate.

The input takes the format "(predictor, covariates, data = NULL)":

"predictor" is the name of the predictor "Y" variable, and should be a single string. lr_coefficients only performs regression that involves one outcome variable. 

"covariates" is a vector of strings containing the names of all the "X" covariates/parameters.

"data" should be a dataframe containing the data of interest.

The results are returned in a matrix.


## Examples

The dataset used for these examples is "mtcars". "mtcars" originally came from the "Motor Trend Car Road Tests" in the 1974 Motor Trend US Magazine. It is built into base R but is included in this package to be extra sure that these examples will work.

These is a basic examples of how to use the function "lr_coefficients" in this package:

```{r example}

data = mtcars

regressionLinear::lr_coefficients("mpg", c("cyl", "disp", "hp"), data=data)

```

For SLR, the X covariate can be included in a vector, or not. The quotation marks should be included so that the function can be

```{r example}

data = mtcars

regressionLinear::lr_coefficients("drat", "gear", data=data)
regressionLinear::lr_coefficients("drat", c("gear"), data=data)

```

## Comparison against lm()

Comparisons for accuracy:

```{r}

summary(lm(mpg~cyl + disp + hp, data=mtcars))
lm(mpg~cyl + disp + hp, data=mtcars)$coef
regressionLinear::lr_coefficients("mpg", c("cyl", "disp", "hp"), data=mtcars)

summary(lm(drat~gear, data=mtcars))
regressionLinear::lr_coefficients("drat", "gear", data=mtcars)

```

Comparisons for efficiency:

```{r}

system.time(lm(mpg~cyl+disp+hp+drat+wt+qsec+vs+am+gear+carb, data=mtcars))

system.time(regressionLinear::lr_coefficients("mpg", c("cyl","disp","hp","drat","wt","qsec","vs","am","gear","carb"), data=mtcars))

```
